---
title: '6060 Practice: RMarkdown'
author: "Marian Pitel"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
  html_document:
    toc_depth: '3'
---

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# Code goes in blocks like this

# load libraries
library(tidyverse)
library(apaTables)

#Load data 
analytic_data_female        <- read_csv("analytic_data_female.csv")

```

# Relations among variables for women

Below are the correlations among the variables for women.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
psych::pairs.panels(analytic_data_female)
       
```

\pagebreak

# Distributions

## Distribution of negative affect scores
Below we can see the distribution of negative affect scores is skewed.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.hist.neg <- ggplot(analytic_data_female,aes(neg_affect))
my.hist.neg <- my.hist.neg + geom_histogram(aes(y=..count..),binwidth = 0.10,fill="black",color="black")
my.hist.neg <- my.hist.neg + labs(title="",x="Negative Affect",y="Frequency")
my.hist.neg <- my.hist.neg + coord_cartesian(xlim=c(0,3), ylim = c(0,1200))
my.hist.neg <- my.hist.neg + theme_classic()
my.hist.neg <- my.hist.neg + theme(axis.line.x = element_line(colour = "black", size=0.5,linetype = 'solid'),
                                   axis.line.y=element_line(colour = "black", size=0.5, linetype='solid'))
my.hist.neg <- my.hist.neg + scale_x_continuous (breaks = seq(0,3,by=1))
my.hist.neg <- my.hist.neg + scale_y_continuous (breaks = seq(0,1200,by=300), expand=c(0,0))
print(my.hist.neg)
```

\pagebreak

## Neuroticism Distribution
Below we can see the distribution of neuroticism scores is relatively normal.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.hist <- ggplot(analytic_data_female,aes(Neuroticism))
my.hist <- my.hist + geom_histogram(aes(y=..count..),binwidth = 0.75,fill="black",color="black")
my.hist <- my.hist + labs(title="",x="Neuroticism",y="Frequency")
my.hist <- my.hist + coord_cartesian(xlim=c(0,25), ylim = c(0,1200))
my.hist <- my.hist + theme_classic()
my.hist <- my.hist + theme(axis.line.x = element_line(colour = "black", size=0.5,linetype = 'solid'),
                           axis.line.y=element_line(colour = "black", size=0.5, linetype='solid'))
my.hist <- my.hist + scale_x_continuous( breaks = seq(0,25,by=5) )
my.hist <- my.hist + scale_y_continuous( breaks = seq(0,1200,by=300),expand=c(0,0))
print(my.hist)
```

\pagebreak

# Relations among variables 
##Scatter plot for Negative Affect and Neuroticism 
Below you can see the correlation between negative affect and neuroticism with a regression line. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.plot.neg.neur <- qplot(neg_affect,Neuroticism,data=analytic_data_female)
my.plot.neg.neur <- my.plot.neg.neur + geom_smooth(method = "lm", se = FALSE, color='black')
my.plot.neg.neur <- my.plot.neg.neur + theme_classic()
my.plot.neg.neur <- my.plot.neg.neur + theme(axis.line.x = element_line(colour='black',size=0.5,linetype='solid'),axis.line.y = element_line(colour='black',size=0.5,linetype='solid'))
my.plot.neg.neur <- my.plot.neg.neur + labs(title="",x="Negative Affect",y="Neuroticism")
my.plot.neg.neur <- my.plot.neg.neur + coord_cartesian(xlim=c(0,3),ylim=c(0,24))
print(my.plot.neg.neur)
```



